\appendix
\label{Appendix}
\settocdepth{chapter}
\input{Parts/Tests.tex}
\input{Code/Makefile.tex}
\input{Code/.tex}

\section{Opgave 3 output}
\label{O3_Output}
~/BOSC/oo2/prod_cons\$ ./prodcons 5 3 3 10 15
Producer 1 produced ITEM_0. Items in buffer: 1 (out of 10)
Producer 2 produced ITEM_1. Items in buffer: 2 (out of 10)
Consumer 2 consumed ITEM_0. Items in buffer: 1 (out of 10)
Consumer 1 consumed ITEM_1. Items in buffer: 0 (out of 10)
Producer 0 produced ITEM_2. Items in buffer: 1 (out of 10)
Consumer 0 consumed ITEM_2. Items in buffer: 0 (out of 10)
Producer 1 produced ITEM_3. Items in buffer: 1 (out of 10)
Consumer 2 consumed ITEM_3. Items in buffer: 0 (out of 10)
Producer 0 produced ITEM_4. Items in buffer: 1 (out of 10)
Consumer 0 consumed ITEM_4. Items in buffer: 0 (out of 10)
Producer 0 produced ITEM_5. Items in buffer: 1 (out of 10)
Consumer 1 consumed ITEM_5. Items in buffer: 0 (out of 10)
Producer 1 produced ITEM_6. Items in buffer: 1 (out of 10)
Producer 2 produced ITEM_7. Items in buffer: 2 (out of 10)
Producer 0 produced ITEM_8. Items in buffer: 3 (out of 10)
Consumer 2 consumed ITEM_6. Items in buffer: 2 (out of 10)
Consumer 0 consumed ITEM_7. Items in buffer: 1 (out of 10)
Consumer 1 consumed ITEM_8. Items in buffer: 0 (out of 10)
Producer 1 produced ITEM_9. Items in buffer: 1 (out of 10)
Consumer 0 consumed ITEM_9. Items in buffer: 0 (out of 10)
Producer 1 produced ITEM_10. Items in buffer: 1 (out of 10)
Consumer 0 consumed ITEM_10. Items in buffer: 0 (out of 10)
Producer 2 produced ITEM_11. Items in buffer: 1 (out of 10)
Producer 0 produced ITEM_12. Items in buffer: 2 (out of 10)
Consumer 2 consumed ITEM_11. Items in buffer: 1 (out of 10)
Consumer 1 consumed ITEM_12. Items in buffer: 0 (out of 10)
Producer 0 produced ITEM_13. Items in buffer: 1 (out of 10)
Producer 2 produced ITEM_14. Items in buffer: 2 (out of 10)
Consumer 0 consumed ITEM_13. Items in buffer: 1 (out of 10)
Consumer 1 consumed ITEM_14. Items in buffer: 0 (out of 10)
